\documentclass[12pt]{article}
%
%Margin - 1 inch on all sides
%
\usepackage[letterpaper]{geometry}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

%
%Doublespacing
%
\usepackage{setspace}
\doublespacing
%Setting the font
\usepackage{times}
%Rotating tables (e.g. sideways when too long)
\usepackage{rotating}
%For multiple rows in tables
\usepackage{multirow}
%url references
\usepackage{url}

\setlength\headsep{0.333in}
%
%Works cited environment
%(to start, use \begin{sources...}, each entry preceded by \bibent)
% - from Ryan Alcock's MLA style file
%
\newcommand{\bibent}{\noindent \hangindent 40pt}
\newenvironment{sources}{}{}

%
%Begin document
%
\begin{document}
\begin{flushleft}
%%%%First page name, class, etc

Jordan Bayles\\
Mike Rosulek\\
ECE 478: Network Security\\
\today\\

%%%%Changes paragraph indentation to 0.5in
\setlength{\parindent}{0.5in}
%%%%Begin body of paper here

\section{Group members}
\begin{itemize}
	\item Jordan Bayles
	\item John Zeller
\end{itemize}

\section{Project Proposal}
Due to both of having a desire to learn more about WEP/WPA wifi
protocols and their vulnerabilities, our project proposal is
to compare and contrast the vulnerabilities present in these
protocols, potentially in a chronological fashion. We will focus
primarily on the different exploits for WEP, WPA, and WPA2 and
potentially go into more detail about AES and TKIP, as well
as more exotic stuff like WPA RADIUS.

\section{Sources to use}
%%%%Works cited
\begin{sources}
\bibent
Lashkari, A.H.; Danesh, M.M.S.; Samadi, B., "A survey on wireless security protocols (WEP, WPA and WPA2/802.11i)," Computer Science and Information Technology, 2009. ICCSIT 2009. 2nd IEEE International Conference on , vol., no., pp.48,52, 8-11 Aug. 2009
doi: 10.1109/ICCSIT.2009.5234856
\\\textbf{URL:} \url{http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=5234856&isnumber=5234374}

\bibent
Majstor, F., "WLAN security threats \& solutions," Local Computer Networks, 2003. LCN '03. Proceedings. 28th Annual IEEE International Conference on , vol., no., pp.650,, 20-24 Oct. 2003
doi: 10.1109/LCN.2003.1243197
\\\textbf{URL:} \url{http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=1243197&isnumber=27859}

\bibent
Wang Shunman; Tao Ran; Wang Yue; Zhang Ji, "WLAN and it's security problems," Parallel and Distributed Computing, Applications and Technologies, 2003. PDCAT'2003. Proceedings of the Fourth International Conference on , vol., no., pp.241,244, 27-29 Aug. 2003
doi: 10.1109/PDCAT.2003.1236297
\\\textbf{URL:} \url{http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=1236297&isnumber=27719}

\end{sources}
\end{flushleft}
\end{document}
